\section{Referencias}

\subsection{Estándares y Normas}

\begin{enumerate}
    \item \textbf{IEEE Std 830-1998}, \textit{IEEE Recommended Practice for Software Requirements Specifications}. Institute of Electrical and Electronics Engineers, 1998.

    \item \textbf{ISO/IEC 25010:2011}, \textit{Systems and software engineering -- Systems and software Quality Requirements and Evaluation (SQuaRE) -- System and software quality models}. International Organization for Standardization, 2011.

    \item \textbf{ISO/IEC 25040:2011}, \textit{Systems and software engineering -- Systems and software Quality Requirements and Evaluation (SQuaRE) -- Evaluation process}. International Organization for Standardization, 2011.

    \item \textbf{PCI DSS v4.0}, \textit{Payment Card Industry Data Security Standard}. PCI Security Standards Council, 2022.

    \item \textbf{WCAG 2.1}, \textit{Web Content Accessibility Guidelines 2.1}. W3C, 2018. Disponible en: \url{https://www.w3.org/TR/WCAG21/}

    \item \textbf{RFC 6749}, \textit{The OAuth 2.0 Authorization Framework}. IETF, 2012. Disponible en: \url{https://tools.ietf.org/html/rfc6749}

    \item \textbf{RFC 8259}, \textit{The JavaScript Object Notation (JSON) Data Interchange Format}. IETF, 2017. Disponible en: \url{https://tools.ietf.org/html/rfc8259}

    \item \textbf{OpenAPI Specification 3.0}, \textit{OpenAPI Initiative}. Linux Foundation, 2023. Disponible en: \url{https://spec.openapis.org/oas/v3.0.3}
\end{enumerate}

\subsection{Regulaciones y Cumplimiento}

\begin{enumerate}
    \item \textbf{GDPR (General Data Protection Regulation)}, \textit{Regulation (EU) 2016/679}. European Parliament and Council, 2016.

    \item \textbf{CCPA (California Consumer Privacy Act)}, \textit{California Civil Code Section 1798.100 et seq}. State of California, 2018.

    \item \textbf{Ley 1581 de 2012}, \textit{Ley de Protección de Datos Personales}. República de Colombia. Disponible en: \url{https://www.sic.gov.co/ley-de-proteccion-de-datos-personales}
\end{enumerate}

\subsection{Metodologías y Frameworks}

\begin{enumerate}
    \item \textbf{Cohn, M.} (2004). \textit{User Stories Applied: For Agile Software Development}. Addison-Wesley Professional.

    \item \textbf{Moscow Method}, \textit{Agile Business Consortium}. Disponible en: \url{https://www.agilebusiness.org/page/ProjectFramework_10_MoSCoWPrioritisation}

    \item \textbf{Domain-Driven Design (DDD)}, Evans, E. (2003). \textit{Domain-Driven Design: Tackling Complexity in the Heart of Software}. Addison-Wesley.

    \item \textbf{RESTful Web Services}, Richardson, L., Ruby, S. (2007). \textit{RESTful Web Services}. O'Reilly Media.

    \item \textbf{Microservices Patterns}, Richardson, C. (2018). \textit{Microservices Patterns: With examples in Java}. Manning Publications.
\end{enumerate}

\subsection{Documentación Técnica de Proveedores}

\begin{enumerate}
    \item \textbf{Stripe API Documentation}. Stripe, Inc. Disponible en: \url{https://stripe.com/docs/api}

    \item \textbf{Firebase Cloud Messaging (FCM) Documentation}. Google. Disponible en: \url{https://firebase.google.com/docs/cloud-messaging}

    \item \textbf{Elasticsearch Reference}. Elastic N.V. Disponible en: \url{https://www.elastic.co/guide/en/elasticsearch/reference/current/index.html}

    \item \textbf{AWS Documentation}. Amazon Web Services. Disponible en: \url{https://docs.aws.amazon.com/}

    \item \textbf{Twilio API Documentation}. Twilio Inc. Disponible en: \url{https://www.twilio.com/docs}
\end{enumerate}

\subsection{Benchmarks y Estudios de Mercado}

\begin{enumerate}
    \item \textbf{Baymard Institute} (2023). \textit{E-commerce Checkout Usability}. Disponible en: \url{https://baymard.com/checkout-usability}

    \item \textbf{Google/SOASTA} (2017). \textit{The Need for Mobile Speed: How Mobile Latency Impacts Publisher Revenue}. Google Inc.

    \item \textbf{Akamai} (2017). \textit{Online Retail Performance Report: Milliseconds Are Critical}. Akamai Technologies.

    \item \textbf{Klarna Insights} (2022). \textit{The Impact of Buy Now Pay Later on E-commerce Conversion}. Klarna Bank AB.

    \item \textbf{Statista} (2023). \textit{E-commerce worldwide - Statistics \& Facts}. Disponible en: \url{https://www.statista.com/topics/871/online-shopping/}
\end{enumerate}

\subsection{Herramientas de Desarrollo y Testing}

\begin{enumerate}
    \item \textbf{OWASP Top 10}, \textit{Open Web Application Security Project}, 2021. Disponible en: \url{https://owasp.org/www-project-top-ten/}

    \item \textbf{Core Web Vitals}, \textit{Google Web Fundamentals}. Disponible en: \url{https://web.dev/vitals/}

    \item \textbf{SonarQube Documentation}, SonarSource SA. Disponible en: \url{https://docs.sonarqube.org/}

    \item \textbf{JMeter User Manual}, Apache Software Foundation. Disponible en: \url{https://jmeter.apache.org/usermanual/index.html}
\end{enumerate}

\subsection{Arquitectura y Patrones}

\begin{enumerate}
    \item \textbf{Fowler, M.} (2014). \textit{Microservices: a definition of this new architectural term}. Disponible en: \url{https://martinfowler.com/articles/microservices.html}

    \item \textbf{Nygard, M.} (2007). \textit{Release It!: Design and Deploy Production-Ready Software}. Pragmatic Bookshelf.

    \item \textbf{Newman, S.} (2015). \textit{Building Microservices: Designing Fine-Grained Systems}. O'Reilly Media.

    \item \textbf{Hohpe, G., Woolf, B.} (2003). \textit{Enterprise Integration Patterns: Designing, Building, and Deploying Messaging Solutions}. Addison-Wesley.
\end{enumerate}

\subsection{Contactos del Proyecto}

\begin{table}[h!]
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Rol} & \textbf{Nombre} & \textbf{Email} \\
\hline
Autor & Nicolas Camacho & camachoa.nicolas@javeriana.edu.co \\
Autor & Sara Albarracín & saalbaracin@javeriana.edu.co \\
Autor & Alejandro Caicedo & caicedo\_alejandro@javeriana.edu.co \\
Autor & Alejandro Pinzón & alejandro\_pinzon@javeriana.edu.co \\
\hline
\end{tabular}
\caption{Equipo de Proyecto AllConnect Market}
\end{table}

\subsection{Control de Versiones del Documento}

\begin{table}[h!]
\centering
\begin{tabular}{|l|l|p{6cm}|l|}
\hline
\textbf{Versión} & \textbf{Fecha} & \textbf{Cambios} & \textbf{Autor} \\
\hline
1.0 & 2025-01-10 & Versión inicial del SRS & Equipo \\
\hline
2.0 & 2025-01-19 & Correcciones según retroalimentación del evaluador: \newline
- Diagrama de contexto completo \newline
- Desglose detallado de RF/RNF \newline
- Priorización MoSCoW \newline
- Modelo de calidad ISO 25010 \newline
- Historias de usuario expandidas \newline
- Interfaces externas detalladas & Equipo \\
\hline
\end{tabular}
\caption{Historial de Versiones del SRS}
\end{table}
